---
title: Library Labs
output: 
  html_document
htmlwidgets: TRUE
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("rmd_config.R")
library(jsonlite)
library(tidyverse)
library(knitr)
```


## How to contribute


We would like this to be a community driven page. 

You can contribute in several ways:

## Update your data
Maybe we have gotten your data wrong. Maybe there is simply something missing.

Go to the [repo](https://github.com/KUBDatalab/Library-labs), and place pull request for a change in the json-file
corresponding to your lab. The relevant file is listed in the table below.

## Add your data

Maybe we have forgotten about you. Maybe we simply did not know that you 
exist. Or maybe we have not got to you yet.

Go to the [repo](https://github.com/KUBDatalab/Library-labs), grab the template 
json-file, fill out your information, and place a pull request for adding the file.

Instructions on what should be added are (will be) in the template. 
Try to keep special characters and whitespace out of the filename.

## Contribute to the project.
This was hacked together during a couple of afternoons, including the time
taken to read the *all* the documentation on markdown::render(). 

There are probably an infinity of improvements that can be made.

Fork the project, make it better, make a pull-request. We would be so grateful!

Cheers

Lars & Christian


## Which json-file is mine?


```{r læsfiler, echo = F}
json_files <- list.files(path = "data/", full.names = T)
json_files <- json_files[json_files != "data/template.json"]
json_files %>% 
  as_tibble() %>% 
  mutate(data = map(value, fromJSON)) %>% 
  unnest(data) %>% 
  select("jsonfile" = value, name) %>% 
  unnest(name) %>% 
  kable()
```

KUB Datalab