---
title: Library Labs
output: 
  html_document
htmlwidgets: TRUE
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("rmd_config.R")
library(jsonlite)
library(tidyverse)
library(knitr)
```


## How to contribute


We would like this to be a community driven page. 

You can contribute in several ways:

## Update your data
Maybe we have gotten your data wrong. Maybe there is simply something missing.

Go to the repo, and place pull request for a change in the json-file
corresponding to your lab. The relevant file is listed in the table below.

## Add your data

Maybe we have forgotten about you. Maybe we simply did not know that you 
exist. Or maybe we have not got to you yet.

Go to the repo, grab the template json-file, fill out your information, and 
place at pull request for adding the file.

## Contribute to the project.
This was hacked together during a couple of afternoons, including the time
taken to read the *all* the documentation on markdown::render(). 

There are probably an infinity of improvements that can be made.

Fork the project, make it better, make a pull-request. We would be so grateful!

Cheers

Lars & Christian


## What json-file is mine?


```{r læsfiler}
json_files <- list.files(path = "data/", full.names = T)
json_files <- json_files[json_files != "data/template.json"]
json_files %>% 
  as_tibble() %>% 
  mutate(data = map(value, fromJSON)) %>% 
  unnest(data) %>% 
  select("jsonfile" = value, name) %>% 
  unnest(name) %>% 
  kable()
```

KUB Datalab