---
title: Library Labs - the map!
output: 
  html_document: 
    include-in-header:
      - header.html
htmlwidgets: TRUE
always_allow_html: true
---

In the KUB Datalab, we have considered how to get an overview of some of the digital labs that exist at research libraries.
 
Since we know a little about the possibilities that Github offers, we have decided to build this page with a digital map.

The map can become a collective project, and we hope that colleagues at other digital labs will [Contribute](contribute.html) by adding data.

We have experienced that the development of experience and material is essential to develop quality material that match

the demand and skills of university staff and students, and we hope that the map can contribute to increased communication between library 
staff who develop course material on digital methods.

[Contribute?](contribute.html)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("rmd_config.R")
library(jsonlite)
library(tidyverse)
library(knitr)
library(leaflet)
library(htmltools)
```




```{r læsdata, echo = F, warning=F}
source("readfiles.R")
labdata <- readRDS("labdata.rds")
```

```{r hent_data, echo = F}
data <- labdata  %>% 
  unnest(c("name", "type", "Description", "link", "Institution"))
```

## Et argument for en eller anden form for kontrol af typer



```{r grupperet_kort, echo=F}
data.type.df <- labdata  %>% 
  select(rowname, name, type, coordinates) %>% 
  unnest(c("coordinates")) %>% 
  unnest(c(lat, lon, type)) %>% 
  mutate(detaljer = paste0('<a href="https://kubdatalab.github.io/Library-labs/listing.html#', rowname, '">', name, '</a>' ))
  


data.type.df <- split(data.type.df, data.type.df$type)

l <- leaflet() %>% 
  addTiles()

   names(data.type.df) %>% 
     purrr::walk(function(df){
       l <<- l %>% 
         addMarkers(data = data.type.df[[df]],
       lng = ~lon, lat = ~lat,
       popup = ~detaljer,
       group = df)
     })



  l %>% 
  addLayersControl(
    overlayGroups = names(data.type.df)
  )
```


## Kontakt mails

```{r echo = F}
data %>% 
  select(name, `Contact email`) %>% 
  unnest(`Contact email`) %>% 
  kable()

```
## hjemmesider

```{r hjemmeside_tabel, echo = F}
data %>% 
  select(name, link) %>% 
    mutate(link = paste0("[",link,"](", link, ")")) %>% 
  kable()
```

## Aktivitetskalendere

```{r echo = F}
data %>% 
  select(name, `Activity calendar`) %>% 
  unnest(`Activity calendar`) %>% 
  mutate(`Activity calendar` = paste0("[",`Activity calendar`,"](", `Activity calendar`, ")")) %>% 
  kable()
```
